%-------------------------
% Resume in Latex
% Author : Eduard Fiego
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

%\newcommand{\resumeItem}[1]{
%  \item\small{
%    {\textbf{#1} \vspace{-2pt}}
%  }
%}

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Eduard Fiego} \\ \vspace{1pt}
    \small +34 674078947 $|$ \href{mailto:eduardfz07@gmail.com}{\underline{eduardfz07@gmail.com}} $|$
    \href{https://www.linkedin.com/in/eduard-fiego-737667237/}{\underline{linkedin.com/in/eduard-fiego}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Embedded Software Engineer - Product Engineer}{July 2024 -- Present}
      {KOSTAL Automobil Elektrik Spain - Between Technology}{Polinyà, BCN}
      \resumeItemListStart
        \resumeItem{AUTOSAR Embedded Software}
        {Collaborated in AUTOSAR Embedded Software projects, especially in their later stages, ensuring the quality standards of the software were met.}
        \resumeItem{Cybersecurity}
        {Collaborated on the cybersecurity implementation of said projects, with a Hardware Security Module (HSM) performing the cryptographic operations and sharing the information with the main application's core.}
        \resumeItem{Software Architecture}
        {Participated in Software Architecture activities, filling gaps and supporting in defining best-practises.}
        \resumeItem{Solution design}
        {Analyzed weaknesses in the currently available tools and designed and implemented solutions to cover said aspects.}
        \resumeItem{Microcontrollers}
        {Obtained experience using the AURIX TC3xx microcontroller from INFINION, mainly on the Watchdog configuration and alarm handling.}
      \resumeItemListEnd

    \resumeSubheading
      {Embedded Software Engineer - Product Engineer}{June 2022 -- July 2024}
      {IDNEO Technologies, SAU}{Mollet del Vallès, BCN}
      \resumeItemListStart
        \resumeItem{Bring-up of technologies and peripherals}
        {CAN, LIN, Spi, I2C, SBC, Adc, external and internal Watchdogs, etc.}
        \resumeItem{AUTOSAR}{
        Using tool chains like VECTOR's DaVinci and ETA's ISOLAR.}
        \resumeItem{Bootloaders}{
        Experience designing and implementing Bootloaders.}
        \resumeItem{Multicore}{
        Experience integrating Multicore architectures into projects.}
        \resumeItem{Microcontrollers}{
        Experience using NXP and ST microcontrollers (S32K3xx, SPC58).}
      \resumeItemListEnd
  \resumeSubHeadingListEnd





%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming languages}{: C, Assembler, C++, Python, Bash, Matlab, Simulink...} \\
     \textbf{Software integration}{: Designed and implemented Sofware Integration Tests and Unitary Tests.} \\
     \textbf{Versioning tools}{: SVN, GIT.} \\
     \textbf{Linux Kernel}{} \\
     \textbf{MISRA-C}{} \\
     \textbf{ASPICE}{} \\
     \textbf{RTOS}{} \\

    }}
 \end{itemize}

 %-----------SOFT SKILLS-----------
\section{Soft Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Communication}{: Trained communication skills, working with teams, and interacting directly with the customers and stakeholders, both in technical and non-technical contexts. } \\
     \textbf{Versatility}{: Highly adaptable and a quick learner.} \\
     \textbf{Leadership}{: Experience in leading projects, making technical and non-technical decisions.} \\
     \textbf{Team player}{: Enjoy working with teams and collaborating with colleagues, trying to extend a helping hand where needed.} \\
     \textbf{Problem solver}{: Passionate about finding solutions to problems, often requiring researching the different possible options and thinking out of the box.} \\
    }}
 \end{itemize}

 %-----------LANGUAGES-----------
\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{English}{ } \\
     \textbf{Catalan}{ } \\
     \textbf{Spanish}{ } \\
    }}
 \end{itemize}

 %-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor's Degree in Computer Engineering}{}
      {Universitat Politècnica de Catalunya (UPC)}{}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
